---
title: "Banknoten"
author: "JoKeYa"
date: "08/05/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ddalpha)
library(ggplot2)
library(randomForest)
library(caret)
```


## Setup
Als Library wurde ddalpha verwendet.
Als Datenset verwenden wir Banknoten.
```{r get_data}
data("banknoten")
data("iris")
plot(banknoten, col = banknoten$falsch)
```

Da die Klassifikation ein Integer ist, kann es wie oben vorkommen, dass der Wert nicht korrekt interpretiert werden kann.
Somit muss die Klassifikation zu einem Faktor übersetzt werden.
```{r set_factor}
banknoten$faktor <- as.factor(banknoten$falsch)
plot(banknoten, col = banknoten$faktor)
```
Länge: Länge der Banknote
Links: Höhe der Banknote bei der linken Seite
Rechts: Höhe der Banknote bei der rechten Seite
Oben: Distanz zwischen inneren Bereich und oberen Rand
Unten: Distanz zwischen inneren Bereich und unteren Rand
Diagonal: Diagonale Länge der Banknote

## Load and visualise the data 


```{r banknoten}
head(banknoten)

str(banknoten)

```

Get help from google to understand what is meant by sepal/petal length and width. 

An excellent introduction in plotting data using iris data 
is available on the site: 
https://www.kaggle.com/antoniolopez/iris-data-visualization-with-r

```{r means, quantils etc}

colMeans(banknoten[,1:7])

median(banknoten$laenge)
median(banknoten$links)
median(banknoten$rechts)
median(banknoten$unten)
median(banknoten$oben)
median(banknoten$diagonal)
median(banknoten$falsch)


# The following command will give the 25% Quantile for Sepal.Length
quantile(banknoten$diagonal, 0.25)

```

I plot the data for the predictor Petal.Length as an example.
And I add the information for the mean (red line), the median (green line) and 25% / 75% quantile (blue and yellow line) in the same plot


Banknoten$falsch wird nicht mehr benötigt und kann die Statistik über den Haufen werfne.
Somit wurde es meinerseits entfernt.
```{r removeFalsch}
banknoten$falsch = NULL

```

```{r, plot faktor}

ggplot(banknoten, aes(x=diagonal, colour=faktor, fill=faktor)) +
  geom_density(alpha=.3) +
  geom_vline(aes(xintercept=mean(diagonal,
                 colour=faktor)), color="red", size=1) +
  geom_vline(aes(xintercept=median(diagonal,
                 colour=faktor)), color="green", size=1) +
  geom_vline(aes(xintercept=quantile(diagonal, 0.25),
                 colour=faktor), color="blue", size=1) +
  geom_vline(aes(xintercept=quantile(diagonal, 0.75),
                 colour=faktor), color="yellow", size=1) +
  xlab("Diagonale") +  
  ylab("Faktor") +
  theme(legend.position="none")
  
```


## Partition the data in training and test sets


```{r partition}
#set.seed to ensure reproducability
set.seed(13) 
trainIndex <- createDataPartition(banknoten$faktor, p = .6, 
                                  list = FALSE, times = 1)

trainSet <- banknoten[trainIndex, ]
testSet <- banknoten[-trainIndex,]
```

Make the model and look at the result
```{r randomForest_model}


model <- randomForest(formula = faktor ~ ., data = banknoten)

model

importance(model)
```

Use the model to make a prediction on the test set 
```{r randoForest_predict}
testSet$prediction <- predict(model, testSet[,1:7])
head(testSet)

```

Look at the confusion matrix
```{r confusion matrix}

table(testSet$faktor, testSet$prediction)

```
This model is perfect in predicting the various species. This in not the normal case. 

## Understand and tune the model

The next step is to understand the model and to tune it. 

The following site can be thereby helpful

https://www.datacamp.com/courses/machine-learning-with-tree-based-models-in-r?tap_a=5644-dce66f&tap_s=210732-9d6bbf


